Symmetric Circuits for Rank Gates

### 2018-04-02 sections/symmetric-circuits.tex
I made major changes to the transparency section. I fixed a few typos in the symmetric circuits section.

  Let $W_t$ be the transitive closure of the relation $W$ on $C$. The inductive
  argument gives us that for all $h \in G$ if there exists an output gate $g$
  such that $W_t(h, g)$, then $\pi (h) = h$. Since the circuit contains no
  redundant gates, we have that $G = \bigcup_{\vec{a} \in [n]^q} \{g \in G : W_t
  (g, \Omega(\vec{a}))\}$, and the result follows.
\end{proof}

>>>>

  Let $W_t$ be the transitive closure of the relation $W$ on $C$. The inductive
  argument gives us that for all $h \in G$ if there exists an output gate $g$
  such that $W_t(h, g)$ or $h = g$, then $\pi (h) = h$. Since the circuit
  contains no redundant gates, we have that $G = \bigcup_{\vec{a} \in [n]^q} \{g
  \in G : W_t (g, \Omega(\vec{a}))\}$, and the result follows.
\end{proof}
